---
title: "RCDS_Climate_assignment_emcg"
author: "VanMcG", "Rosanna", "Olivia"
date: "February 3, 2017"
output: html_document
---

##Temperature Data
**Question 1:**  
How are the measurements made? What is the associated measurement uncertainty?  
What is the resolution of the data?
Are their missing values? How should they be handled?

**Question 2:**   
Construct the necessary R code to import and prepare for manipulation the following data set: http://climate.nasa.gov/system/internal_resources/details/original/647_Global_Temperature_Data_File.txt

```{r library, message=FALSE}
library("tidyverse")
#
# This is where our import code will go
```

**Question 3:**  
Plot the trend in global mean temperatures over time. Describe what you see in the plot and how you interpret the patterns you observe.

```{r}
#our plot goes here
```

**Question 4:**  
What additional analyses or data sources would better help you refine your arguments?

**Question 5:**  
What is the meaning of “5 year average” vs “annual average”?  
Construct 5 year averages from the annual data. Construct 10 & 20-year averages.
```{r}
#our mean calcuations go here
```

Plot the different averages and describe what differences you see and why.
```{r}
#our time series plots go here
```


##Melting Ice Sheets?

**Question 1:**  
Describe the data set: what are the columns and units? Where do the numbers come from?  
What is the uncertainty in measurment? Resolution of the data? Interpretation of missing values?

**Question 2:**  
Construct the necessary R code to import this data set as a tidy Table object.
```{r}
#table object code
```

**Question 3:**  
Plot the data and describe the trends you observe.
```{r}
#Plots
```


##Rising Sea Levels?

**Question 1:**  
Describe the data set: what are the columns and units?  
Where do these data come from?  
What is the uncertainty in measurment? Resolution of the data? Interpretation of missing values?

**Question 2:**  
Construct the necessary R code to import this data set as a tidy Table object.
```{r}
#table object code
```

**Question 3:**  
Plot the data and describe the trends you observe.
```{r}
#Plots
```


##Arctic Sea Ice?
**Question 1:**  
Describe the data set: what are the columns and units?  
Where do these data come from?  
What is the uncertainty in measurment? Resolution of the data? Interpretation of missing values?

**Question 2:**  
Construct the necessary R code to import this data set as a tidy Table object.
```{r}
#table object code
```

**Question 3:**  
Plot the data and describe the trends you observe.
```{r}
#Plots
```


##Longer term trends in CO2 Records
**Questions / Tasks:**  
Describe the data set: what are the columns and units? Where do the numbers come from?  
What is the uncertainty in measurment? Resolution of the data? Interpretation of missing values?  
Read in and prepare data for analysis.
```{r}
#data prep code
```
Reverse the ordering to create a chronological record.  
Plot data
```{r}
#Plots
```
Consider various smoothing windowed averages of the data.
```{r}
#Plots
```
Join this series to Mauna Loa data  
Plot joined data
```{r}
#Plots
```
Describe your conclusions

